Lattice Boltzmann simulations of magnetically responsive\\ anisotropic particle stabilized emulsions

### 2025-03-05 chapters/lit_review.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3

When two partially miscible fluids are mixed together, they will have the tendency to coalesce into two distinct phases as they attempt to minimize 
the thermodynamic penalty accrued from the formation of an interface. To prevent this coalescence process, conventionally small molecule surfactants 
are utilized. The most famous example of this class of material is soap which emulsifies dirt into droplets suspended in water through mechanical action. 
Surfactants function through reducing the surface tension between the droplet, known as the dispersed phase, and the bulk fluid, known as the continuous 
phase. Surfactants function through reducing the surface tension between dispersed and continuous phases, reducing the energy penalty owed from formation 
of an interface.

The existence of particle stabilized emulsions has been known for more than a century now, after Pickering and Ramsden independently identified dispersed 
droplets of oil within a water matrix after vigorous stirring of an oil, water and particle mixture. \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907} 
Unlike surfactants, particles act as emulsion stabilizers through the reduction of contact between dispersed and continuous phases as they adsorb into 
the interface between phases. The Pieranski model derived from observations of \textcolor{blue}{insert derivation of pieranski model} 
and is used to determine the adsorption energy of a particle at an interface. It is defined as $G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2$, where $G_{ads}$ 
is the free energy reduction from a particle adsorption, $\sigma$ is the surface tension between the partially miscible fluids, $\theta_c$ is the contact angle 
of the particle. The particles can be considered to be irreversibly adsorb even for nanoparticles, and for particles larger than 100nm, the adsorption energy 
is so great that thermal fluctuations at the interface can be considered to have no effect. \cite{cheung_molecular_2011}

After their discovery, interest in particle stabilized emulsions became minimal. However, increased interest in them has resurfaced since the 1980s owing to 
their applications in food science. One such example is fat crystals stabilizing water droplets in oil to create margarine. Particle stabilization has also 
been of interest owing to their lower toxicity and greater ease of sustainable sourcing through the usage of cellulose or chitin particles. 
\cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}
Additionally, chemical surfactants can be toxic to aquatic life, acting as a xeno-hormone and interfering with their reproduction. 
\cite{kaczerewska_environmental_2020, lechuga_acute_2016}

Compared to emulsions stabilized using surfactants, particle stabilized emulsions offer greater resistance to coarsening, resulting in increased interest in 
them once again. The microstructure properties of particle stabilized emulsions were explored in the early 2000s by Lumsdon and Binks among many others. They 
observed that the radius of emulsion droplets, $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ are volume fractions of water and particles 
respectively. \cite{binks_pickering_2001} They also identified that there were other techniques to modify the microstructure of a Pickering Emulsion 
such as concentration of fluids and particle wettability. Neutrally wetting particles do not impart a preferential curvature to the interface. When 
using non-neutrally wetting particles, bridged droplets, capillary aggregates and other non droplet microstructures can be observed. Bijels, are synthesized 
in a system using equal volume fraction of fluids and neutrally wetting particles, thus facilitating the formation of tortuous, co-continuous domains.

Bijels are synthesized in systems which have roughly equal fluid volume fractions and neutrally wetting particles so as to not impose preferential 
curvature on the interface. \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015} 
Reeves et al. demonstrated that bijels stabilized with nanoparticles are more stable than those with microparticles due to better mechanical properties and 
interface coverage. \cite{reeves_particle-size_2015}  Additionally, research by Jansen, Harting, and Hijnen et al. showed that the bijel domain size 
$L \propto \frac{1}{\phi_p}$ for both rod-like and spherical particles. Although the pre-factor is dependent upon the particle geometry, this feature 
has been seen with many other particle shapes as well. \cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, 
loudet_capillary_2005, cheng_shape-anisotropic_2013}

@@

In the past decade, methods to synthesize particles which have anisotropic geometry and chemistry have increased in number and scope. Synthesis techniques vary 
depending on the type of particle shape desired. Ellipsoids can be easily created by mechanical deformation of polymer spheres. Dumbbell shaped particles can be 
synthesized using microfluidic devices or emulsion templating. Square particles can be generated using crystallization of material. \cite{morgan_understanding_2013} 
These variety of techniques mean that particle geometry is no longer as constraint when investigating prospective particle stabilizers of bijels. 
\cite{wu_recent_2016}

Anisotropic particles have shape dependent properties owing to their induction of multipolar interactions by deforming the interface to ensure the mean 
curvature is 0,  fulfilling the Young-Laplace equation shown in Figure \ref{fig:anisotropic_particle_interface}. \cite{loudet_capillary_2005, 
cheng_shape-anisotropic_2013} Using this property has enabled directed assembly and migration through modified capillary forces. 
\cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}

@@

When stabilizing bijels, ellipsoidal particles offer greater stability than spherical ones due to their larger cross-sectional area to volume ratio, 
as shown by Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015} This results in additional domain coarsening timescales 
from particle re-orientation and increased mechanical rigidity, enhancing the stability of emulsions with ellipsoidal particles, as evidenced in rheological 
studies. \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013} It has also been shown that particle shape changes how and when jamming occurs. 
Using graphene plate like particles, it was shown that the plate like particles can have their own elasticity to them, affecting when jamming occurs. 
\cite{imperiali_simple_2014, sun_assembly_2013}

Control over the orientation of ellipsoidal particles at interfaces balances interfacial capillary and magnetic field forces. 
\cite{bresme_orientational_2007, davies_assembling_2014} Theory and simulations indicate a critical field strength above which particle orientation 
is dominated by the applied field. \cite{bresme_orientational_2007, davies_assembling_2014} Experiments and simulations have found that steric interactions, 
influenced by orientation and interfacial arrangements significantly influence the free energy of particle assemblies, highlighting the complex interplay 
between these forces. \cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}

@@

Bijels were first synthesized using Thermally Induced Phase Separation (TIPS). \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015} 
First, a small molecule or polymer blend with a critical point, named the casting mixture, is identified and prepared with a composition corresponding to 
that of the critical point. Next, the casting mixture is blended with particle surfactants while still in a single phase. Once the particles are distributed 
homogenously in the casting mixture, phase separation is initiated in the casting mixture through changing the temperature such that it is in the two-phase region. 
Through ensuring the composition is that of the critical point, the casting mixture undergoes spinodal decomposition without any nucleation and growth.

TIPS allows for batch synthesis of bijels in research labs. However to make bijels industrially relevant, a continuous process which also facilitates the 
synthesis of multiple form factors of bijels for various applications. Solvent Transfer Induced Phase Separation (STrIPS) was proposed as a means to do just this. 
A casting mixture composed of two fluids, a co-solvent, particles and a surfactant is prepared. The fluids will constitute the bijel while the co-solvent will 
diffuse out of the bijel to initiate phase separation. The surfactant is present to ensure that the bijel remains stable against Marangoni pressure. The casting 
mixture if extruded into a bath of non-solvent that is not miscible with the bijel constituents but is miscible with the co-solvent. Diffusion of co-solvent 
initiates phase separation and synthesis of the bijel. The concentration of surfactant and the flow rate of the casting mixture control the obtained microstructure.

@@

@@

@@

% STrIPS, shown in Figure \ref{fig:strips}, and many other fabrication techniques require fine control over the composition of the casting mixture for the technique to function and to control the obtained microstructure. \cite{haase_continuous_2015, amirfattahi_fabrication_2024, sprockel_fabrication_2023} In homogenization, the applied shear of mixing initiates coalescence of droplets in a controlled way, leading to formation of the bijel. \cite{cai_bijels_2017} In both synthesis strategies, the rheology of a proposed casting mixture is therefore essential to understand to explore what other casting mixtures can be utilized in these fabrication techniques. Microstructure control has also been achieved when using TIPS by controlling the concentration of particles at different heights, creating a gradient of pore sizes in the final bijel. \cite{french_bicontinuous_2022} Looking to the current state of stimuli response in bijels,

% \begin{wrapfigure}{r}{7cm}
% \caption{Schematic of a bijel with hard-sphere particles undergoing shear, demonstrating migration and detachment of particles at the interface. \cite{bonaccorso_shear_2020}}
% \label{wrap-fig:bijel_under_shear}
% \includegraphics[width=7cm]{figures/literature_review/bijel_under_shear.jpeg}
% \end{wrapfigure}

@@

@@

Studies into bijel rheology have shown the characteristics of a gel when the
storage modulus exceeds the loss modulus. \cite{lee_making_2013, bai_dynamics_2015} Ching and Mohraz also demonstrated that the rheological behaviour of a 
bijel most closely resembles a 2D colloidal glass that was percolating in 3D space by comparing the linear visco-elasticity of bijels with colloidal gels made 
with strongly attractive particles. \cite{ching_bijel_2022} Several key feature of glasses are that they posses a yield stress, viscoelastic behaviour and a 
glass transition point. \cite{pham_yielding_2008, weeks_introduction_2017} Yield stress is the stress imparted when the particle monolayer is irreversibly changed. \cite{pham_yielding_2008} Viscoelasticity is present when the particle monolayer has solid and a liquid like behaviour, depending upon the timescale of the applied stress. \cite{pham_yielding_2008} The glass transition point is characterized when the dynamics of the monolayer drastically slow down. \cite{weeks_introduction_2017} Figure \ref{fig:bijel_under_shear} demonstrates Bonnacorso et al.'s findings that when subjecting a bijel stabilized with hard-sphere like spherical particles to shear, the particles align to the direction of applied shear before detaching from the interface. \cite{bonaccorso_shear_2020} Looking to how particle alignment affects rheology, past work in suspension rheology has shown that colloidal systems with hard-sphere interparticle interactions undergoing constant shear demonstrate particle ordering (shear banding) in the direction of shear at moderate shear rates, causing shear thinning. \cite{vermant_flow-induced_2005, brader_nonlinear_2010}

@@

Five primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or 
interparticle potential model  will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities,

In addition to the Shan-Chen model, the color gradient model, free energy model, mean field theory model and interface tracking technique all 
allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
simplicity and ease of implementation. The mean field theory

>>>>

When two partially miscible fluids are mixed, they tend to separate into distinct phases to minimize the thermodynamic penalty associated with interfacial formation. 
To inhibit this phase separation, small-molecule surfactants are conventionally employed. A well-known example of such a material is soap, which facilitates the 
emulsification of dirt into droplets suspended in water through mechanical agitation. Surfactants function by reducing the surface tension between the dispersed 
phase (droplets) and the continuous phase (bulk fluid), thereby lowering the interfacial energy penalty associated with phase formation.

The existence of particle-stabilized emulsions has been recognized for over a century, following the independent discoveries by Pickering and Ramsden, who observed dispersed 
oil droplets within a water matrix after vigorous stirring of an oil-water-particle mixture \cite{ramsden_separation_1904, pickering_cxcvi.emulsions_1907}. Unlike surfactants, 
which stabilize emulsions by reducing interfacial tension, particles act as stabilizers by adsorbing at the interface between the dispersed and continuous phases, thereby 
preventing direct contact between them. The Pieranski model, derived from \textcolor{blue}{insert derivation of Pieranski model}, is commonly used to determine the adsorption 
energy of a particle at an interface. It is expressed as $ G_{ads} = \sigma A_{rm} (1 - \cos{\theta_c})^2 $ where $G_{ads}$ represents the free energy reduction upon particle 
adsorption, $\sigma$ is the surface tension between the partially miscible fluids, and $ \theta_c $ is the contact angle of the particle. Particles at the interface are 
generally considered irreversibly adsorbed, even at the nanoscale. For particles larger than 100 nm, the adsorption energy is sufficiently high that thermal fluctuations at 
the interface can be considered negligible \cite{cheung_molecular_2011}.

Following their initial discovery, interest in particle-stabilized emulsions waned for several decades. However, since the 1980s, renewed attention has emerged due to 
their applications in food science. A notable example is the stabilization of water droplets in oil by fat crystals, a process used in margarine production. Particle 
stabilization has also gained interest due to its lower toxicity and the potential for sustainable sourcing, particularly through the use of cellulose or chitin 
particles \cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}. Moreover, conventional chemical surfactants pose 
environmental concerns, as they can be toxic to aquatic life, acting as xeno-hormones and disrupting reproductive processes 
\cite{kaczerewska_environmental_2020, lechuga_acute_2016}.

Compared to surfactant-stabilized emulsions, particle-stabilized emulsions exhibit greater resistance to coarsening, leading to renewed interest in their applications. 
The microstructural properties of these emulsions were extensively studied in the early 2000s by Lumsdon, Binks, and others. Their findings indicated that the emulsion 
droplet radius follows the relationship $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ represent the volume fractions of water and particles, 
respectively \cite{binks_pickering_2001}. Additionally, they identified several factors influencing the microstructure of Pickering emulsions, including fluid concentration 
and particle wettability. Neutrally wetting particles do not impose a preferential curvature on the interface, whereas non-neutrally wetting particles can lead to the 
formation of bridged droplets, capillary aggregates, and other non-spherical microstructures. A notable example is bijels, which are synthesized in systems containing equal 
volume fractions of immiscible fluids and neutrally wetting particles, leading to the formation of tortuous, co-continuous domains.

Bijels are synthesized in systems containing approximately equal fluid volume fractions and neutrally wetting particles to prevent the imposition of preferential 
curvature at the interface \cite{stratford_colloidal_2005, herzig_bicontinuous_2007, lee_bicontinuous_2010, jansen_bijels_2011, velankar_non-equilibrium_2015}. 
Reeves et al. demonstrated that bijels stabilized with nanoparticles exhibit greater stability than those stabilized with microparticles due to enhanced mechanical 
properties and improved interfacial coverage \cite{reeves_particle-size_2015}. 
Furthermore, research by Jansen, Harting, and Hijnen et al. established that the bijel domain size follows the relationship $ L \propto \frac{1}{\phi_p} $ for both 
rod-like and spherical particles. While the proportionality constant depends on particle geometry, this trend has been observed across various particle shapes 
\cite{hijnen_bijels_2015, madivala_exploiting_2009, gunther_timescales_2014, daware_emulsions_2015, loudet_capillary_2005, cheng_shape-anisotropic_2013}.

@@

Over the past decade, advancements in synthesis techniques have significantly expanded the ability to fabricate particles with anisotropic geometry and surface chemistry. 
The choice of synthesis method depends on the desired particle shape. For example, ellipsoidal particles can be readily produced through the mechanical deformation of 
polymer spheres, while dumbbell-shaped particles can be synthesized using microfluidic devices or emulsion templating. Square-shaped particles, on the other hand, can be 
generated through controlled crystallization \cite{morgan_understanding_2013}. The increasing variety of synthesis methods has reduced geometric constraints when exploring 
potential particle stabilizers for bijels \cite{wu_recent_2016}.

Anisotropic particles exhibit shape-dependent properties due to their ability to induce multipolar interactions by deforming the interface to maintain a mean curvature of 
zero, thereby satisfying the Young-Laplace equation, as illustrated in Figure \ref{fig:anisotropic_particle_interface} \cite{loudet_capillary_2005, cheng_shape-anisotropic_2013}.
This property has been leveraged to facilitate directed assembly and migration through modified capillary forces 
\cite{cavallaro_curvature-driven_2011, read_dimerization_2020, sharifi-mood_curvature_2015}.

@@

When stabilizing bijels, ellipsoidal particles provide greater stability than spherical ones due to their higher cross-sectional area-to-volume ratio, as demonstrated by 
Günther et al. and Hijnen et al. \cite{gunther_timescales_2014, hijnen_bijels_2015}. This enhanced stability arises from additional domain coarsening timescales associated 
with particle reorientation and increased mechanical rigidity, as confirmed by rheological studies \cite{gunther_timescales_2014, daware_emulsions_2015, witt_bijel_2013}. 
Furthermore, particle shape influences both the onset and dynamics of jamming. Studies using graphene plate-like particles have shown that these particles exhibit intrinsic 
elasticity, which affects the conditions under which jamming occurs \cite{imperiali_simple_2014, sun_assembly_2013}.

The orientation of ellipsoidal particles at interfaces is governed by a balance between interfacial capillary forces and external magnetic fields 
\cite{bresme_orientational_2007, davies_assembling_2014}. Theoretical studies and simulations suggest the existence of a critical field strength beyond which particle 
orientation is predominantly dictated by the applied field \cite{bresme_orientational_2007, davies_assembling_2014}. Additionally, both experimental and computational 
studies have shown that steric interactions—modulated by particle orientation and interfacial arrangements—play a significant role in determining the free energy of particle 
assemblies, underscoring the intricate interplay between these forces \cite{morgan_understanding_2013, newton_influence_2014, newton_capillary_2018}.

@@

Bijels were first synthesized using Thermally Induced Phase Separation (TIPS) \cite{herzig_bicontinuous_2007, lee_bicontinuous_2010, bai_dynamics_2015}. 
The process begins by identifying a small-molecule or polymer blend with a critical point, referred to as the casting mixture, and preparing it at a composition 
corresponding to this critical point. The casting mixture is then combined with particle surfactants while remaining in a single-phase state. Once the particles 
are homogeneously distributed, phase separation is induced by adjusting the temperature to bring the system into the two-phase region. By ensuring that the 
composition aligns with the critical point, the casting mixture undergoes spinodal decomposition, preventing nucleation and growth.

TIPS enables batch synthesis of bijels in research laboratories. However, for bijels to become industrially viable, a continuous fabrication process is required—one 
that also allows for the production of various bijel form factors suited to different applications. Solvent Transfer Induced Phase Separation (STrIPS) has been proposed 
as a method to achieve this. In STrIPS, a casting mixture is prepared, consisting of two fluids that form the bijel, a co-solvent, particles, and a surfactant. Phase 
separation is initiated as the co-solvent diffuses out of the bijel. The surfactant is included to maintain bijel stability against Marangoni forces. The casting mixture 
is then extruded into a bath of a non-solvent, which is immiscible with the bijel-forming fluids but miscible with the co-solvent. The diffusion of the co-solvent triggers 
phase separation, leading to bijel formation. The resulting microstructure is influenced by both the surfactant concentration and the flow rate of the casting mixture.

@@

Vapor Induced Phase Separation(VIPS) has also been identified as a technique for continuous fabrication of bijels. \cite{wang_scalable_2020} A quarternary casting mixture
containing particles, solvent and two partially miscible liquids is prepared. The solvent and liquid species are carefully selected to ensure that removal of the
solvent will cause phase separation of the two partially miscible liquids. One system that has been used is the water/hexanediol-diacrylate solvated by ethanol.
Selection of the composition of the system facilitates crossing of the binodal through the critical point, causing phase separation through spinodal decomposition.
This technique has been used to fabricate thin films of bijels blade and spray coated onto substrates.

@@

Instead of relying upon spinodal decomposition to generate the bijel morphology, homogenization uses shear to join phase separating domains, resulting in a 
structure that has the properties of a bijel even if not fabricated from fluids undergoing spinodal decomposition. \cite{huang_bicontinuous_2017, cai_bijels_2017} 
This method is primarily used for nanoparticles under $50$ nm and it has been shown to work for multiple particle geometries. This method relies upon
shear to cause limited coalescence of droplets. As coarsening occurs, particles adsorb on the interface and when the interfacial area matches the area of the
adsorbed particles, the microstructure jams. Tuning of the method can be done through modifying the contact angle of the particles at the interface as well as
the viscosity of the fluids.

@@

Enter something about this method. \cite{amirfattahi_fabrication_2024}

@@

Bijels undergoing constant shear demonstrate shear thinning behavior which at moderate shear rates can be described reasonably well using the Herschel-Buckley
model. \cite{macmillan_rheological_2019, wang_morphology_2023} At higher shear rates, the bijel microstructure is destroyed and the viscosity becomes newtonian. 
\cite{cai_bijels_2017,bonaccorso_shear_2020}. Figure \ref{fig:bijel_under_shear} illustrates the findings of Bonnacorso et al., which observed that when a bijel 
stabilized with hard-sphere-like particles is subjected to shear, the particles initially align with the shear direction before detaching from the interface 
\cite{bonaccorso_shear_2020}. Investigating the impact of particle alignment on rheology, prior studies in suspension rheology have shown that colloidal systems 
with hard-sphere interparticle interactions undergoing constant shear exhibit shear banding—where particles order in the shear direction at moderate shear rates—resulting 
in shear thinning \cite{vermant_flow-induced_2005, brader_nonlinear_2010}.

@@

Studies on complex bijel rheology have demonstrated gel-like characteristics when the storage modulus exceeds the loss modulus \cite{lee_making_2013, bai_dynamics_2015}. 
Ching and Mohraz further showed that the rheological behavior of bijels closely resembles that of a 2D colloidal glass percolating in 3D space, based on comparisons of 
linear viscoelasticity with colloidal gels composed of strongly attractive particles \cite{ching_bijel_2022}. Key characteristics of glasses include the presence of a 
yield stress, viscoelastic behavior, and a glass transition point \cite{pham_yielding_2008, weeks_introduction_2017}. Yield stress corresponds to the applied stress at 
which the particle monolayer undergoes irreversible structural changes \cite{pham_yielding_2008}. Viscoelasticity arises when the monolayer exhibits both solid and 
liquid-like behavior, depending on the timescale of the applied stress \cite{pham_yielding_2008}. The glass transition point is marked by a dramatic slowdown in the 
monolayer's dynamics \cite{weeks_introduction_2017}.

@@

Four primary techniques to model multicomponent or multiphase systems exist in the LBM literature. A quick review of the Shan-Chen or 
interparticle potential model  will be provided here from the perspective of a binary mixture. Additionally, the names and descriptions of 
other techniques will be described as well. The interparticle potential model or Shan-Chen model that adds a non-local density dependent force 
between two species, effectively modelling non-ideal mixing and recovering the Cahn-Hilliard equation. To alleviate the standard Shan-Chen implementations 
weaknesses of not being thermodynamically consistent and reducing the existence of spurious velocities,

In addition to the Shan-Chen model, the color gradient model, free energy model and interface tracking technique all 
allow for simulations of various types of multiphase and/or multicomponent flows. The color gradient model proposed by Rothman and Keller and 
implemented by Gunstensen et al relies upon modelling two particle distributions. These represent a binary fluid mixture with the collision step 
able to recover the hydrodynamics and non-ideal mixing dynamics. The free energy model utilizes phase field theory and constructs a free energy 
functional to recover interfacial dynamics and effects in a thermodynamically consistent manner. Often, a square gradient free energy is used for 
simplicity and ease of implementation. The mean field theory

### 2025-03-05 chapters/paper1.tex
Changes 1. Reworded introduction and lit review and addressed grammar and vocab issues 2. Fixed some referencing problems in the document 3. Fleshed out introduction in paper 2 4. Added sections for results in paper 3

Magnetic response has been used in particle stabilized emulsions in the past, causing controlled emulsion failure and
on-demand droplet coalescence for encapsulation and cargo release applications. \cite{melle_pickering_2005,zhou_magnetic_2011}
Fields also enable self assembly through the control of interface deformation derived capillary forces.
\cite{morgan_understanding_2012,davies_interface_2014,davies_dipolar_2015} Magnetically responsive spherical particle 
stabilized bijels have thus far not yielded significant microstructural modifications. \cite{kim_bijels_2010} However, 
electric fields have been shown to cause percolating cylindrical domains in electrically responsive bijels. \cite{carmack_tuning_2018}
The electric field causes polar interactions between particles, which causes the formation of chains of particles that
also function as nucleation sites for phase separation. \cite{carmack_tuning_2018}

>>>>

Magnetic response has been used in particle stabilized emulsions in the past, causing controlled emulsion failure and
on-demand droplet coalescence for encapsulation and cargo release applications. \cite{melle_pickering_2005, zhou_magnetic_2011}
Fields also enable self assembly through the control of interface deformation derived capillary forces.
\cite{morgan_understanding_2013,davies_interface_2014,davies_dipolar_2015} Magnetically responsive spherical particle 
stabilized bijels have thus far not yielded significant microstructural modifications. \cite{kim_bijels_2010} However, 
electric fields have been shown to cause percolating cylindrical domains in electrically responsive bijels. \cite{carmack_tuning_2018}
The electric field causes polar interactions between particles, which causes the formation of chains of particles that
also function as nucleation sites for phase separation. \cite{carmack_tuning_2018}
